Reading Notes

### 2020-06-09 paper.tex
reading about force matching -- alternative to IBI

\cite{Reith2003a}
IBI algorithm is made in this paper! Uses potentials of mean force. IBI potentials are nontransferrable--they work best for the system they are optimized for.
CG allows chain behavior to be studied. History: bead spring polymer chains in a melt to a soft-core liquid ellipsoidal particles with anisotropic gaussian potential. polymer melt cg-ing. None of these derived an automated optimization scheme to conserve the chemical nature of the underlying atomistic model in a standardized way as we do.
PRISM theory combined with MC can predict long and short range structures of polymer chains but can't produce CG potentials.
Reverce MC can reproduce RDF without a need for potential. lack of potential limits usefulness though because RMC uses knowledge of RDF without knowing underlying forces.
Description of IBI algorithm: potential of mean force IS boltzmann inversion of RDF. (Free energy NOT potential energy.) Bending potentials before nonbonded potentials.
They used a five point running average to smooth the potentials
bond stretch -> angle bend -> nonbonded -> dihedral
They started with monoatomic liquids with LJ and WCA potentials (1) they used the correct potential as V0. (2) then they used the boltzmann inverse of the RDF. 
Conclusions:
start with small range (cutoff?) and increase until RDF matches. CG FF for polyisoprene are different between solution and melt.
\cite{Ayton2007a}
\cite{Peter2009c}
\cite{Baschnagel2000}
\cite{Brini2013}
\cite{Murtola2009a}
\cite{Peter2009d}

>>>>

\cite{Reith2003a}
IBI algorithm is made in this paper! Uses potentials of mean force. IBI potentials are nontransferrable--they work best for the system they are optimized for.
CG allows chain behavior to be studied. History: bead spring polymer chains in a melt to a soft-core liquid ellipsoidal particles with anisotropic gaussian potential. polymer melt cg-ing. None of these derived an automated optimization scheme to conserve the chemical nature of the underlying atomistic model in a standardized way as we do.
PRISM theory combined with MC can predict long and short range structures of polymer chains but can't produce CG potentials.
Reverce MC can reproduce RDF without a need for potential. lack of potential limits usefulness though because RMC uses knowledge of RDF without knowing underlying forces.
Description of IBI algorithm: potential of mean force IS boltzmann inversion of RDF. (Free energy NOT potential energy.) Bending potentials before nonbonded potentials.
They used a five point running average to smooth the potentials
bond stretch -> angle bend -> nonbonded -> dihedral
They started with monoatomic liquids with LJ and WCA potentials (1) they used the correct potential as V0. (2) then they used the boltzmann inverse of the RDF. 
Conclusions:
start with small range (cutoff?) and increase until RDF matches. CG FF for polyisoprene are different between solution and melt.

\cite{Ayton2007a}
Coarse graining scheme, systematic, for biological systems.
If CGing is done systematicall it retains important averaged atomistic level interations. Connecting length and time scales.Systematic methods for making CG systems: RMC, this paper will focus on multiscale coarse graining (MS-CG) uses force matching algorithm
Variational. Some of the math does not make sense but it appears to only be based on positions of atomistic and CG particles. They make the free energies of the atomisitic and CG systems the same. Many atomistic frames are mapped to CG beads and the potentials are based in the gradient of the forces felt by the beads. The algorithm minimizes a residual function.
Summary: works, RDFs match. Enables calculation of CG force fields without resolving many-dimensional potential of mean force. (but honestly IBI seems so much simpler. Is there something I'm missing? is boltzmann inverse of RDF not PMF?? This paper was published after Reith paper... when is force matching better?)

\cite{Peter2009c}
\cite{Baschnagel2000}
\cite{Brini2013}
\cite{Murtola2009a}
\cite{Peter2009d}
